The importance of measurement uncertainty in ecological management

### 2018-01-04 manuscripts/manuscript.Rmd
theme should work once container updates

```{r suggested_libs}
library(hrbrthemes)
library(extrafont)
##extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
extrafont::loadfonts()
hrbrthemes::import_roboto_condensed()     # One-time use to set up fonts 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

```{r}
all_policies <- read_csv(file.path(log_dir, "all_policies.csv"))
all_policies %>% 
  filter(policy %in% c("low", "medium", "det", "msy")) %>%
  mutate(policy = fct_recode(policy,
                             "MSY" = "msy",
                             "Constant escapement" = "det",
                             "POMDP: low prior" = "low",
                             "POMDP: medium prior" = "medium"
                             )) %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  + 
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```

@@

```{r eval=FALSE}
sims %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", berkeley_colors) ) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

>>>>

```{r suggested_libs}
library(hrbrthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

```{r}
all_policies <- read_csv(file.path(log_dir, "all_policies.csv"))
all_policies %>% 
  filter(policy %in% c("low", "medium", "det", "msy")) %>%
  mutate(policy = fct_recode(policy,
                             "Constant escapement" = "det",
                              "MSY" = "msy",
                             "POMDP: low prior" = "low",
                             "POMDP: medium prior" = "medium"
                             )) %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = c("black", berkeley_colors) ) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8))
```

@@

```{r eval=FALSE}
sims %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", berkeley_colors) ) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```
